Paper Title

### 2020-10-10 Paper/active-learning-interactive.tex
changes in sections

Recent work in machine translation approaches has focused on integrating active learning
with interaction-based neural machine translation. These modifications have been experimentally 
employed with unbounded real-time streaming data \cite{peris2020active} with the objective of selecting 
only those sentences which are very difficult for the translation system to accurately classify upon 
during the initial stages. Results have shown promise in improving the overall quality of translation 
and reducing human intervention in the process. A core component of this approach involves tweaking the 
sampling strategies involved to maximize the probability of selecting only the most “difficult” sentences. 
However, these results have a lack of representation and probable efficacy with respect to low-resource-based 
multilingual paradigms. The effectiveness of slight alterations in the overall encoder-decoder transformer 
network also needs to be experimented upon to possibly generate higher quality translations.

>>>>

\subsection{Active learning for interactive neural machine translation of data streams}
\label{active-learning-interactive}

A series of recent research works discuss and introduce a variety of model- and data-based methods to select the most informative samples to improve an NMT's performance.
\citet{zhang2018active} propose two active learning techniques for sentence selection, based on semantic similarity between the sentence embeddings and decoder probability as a token of translation quality, while \citet{peris2020active} explore the application of active learning methods in the interactive translation of large data streams. The latter work uses the attention mechanism of a neural machine translation system to select only those sentences worthy of human annotation for translation. 
In a more recent approach, \citet{zeng2019empirical} perform an empirical evaluation of different AL methods for Transformers \cite{vaswani2017attention}, analyzing data-driven approaches, that sample instances based only on two sets of labeled and unlabeled sentences, and model-driven methods, which additionally incorporate information from the current model into sampling. 
However their work notes the weak performance of Coverage Sampling compared to the other techniques, due to the complex nature of the state-of-the art multi-layer multi-head Natural Language Processing architectures, a phenomenon we are addressing with the current work.
A series of works explored the shortcomings of Active Learning approaches in Machine Translation. \cite{lowell2018practical} observe the performance drop issues arising in applying Active Learning across different models and tasks and discuss the methods' generalization constraints. Similarly, \citet{koshorek2019limits} examine the potential and limitations of an oracle policy in selecting samples to maximize the performance of a neural machine translation system in learning sentence semantic representations, concluding on a non-significant difference with a random sentence selection approach.
